Real-time Attention Assessment for Social Robots

### 2015-09-15 paper.tex

We predict that there will be no generalizable pattern of participant's VFOA
behavior for different scenarios such as multiple subjects, necessitating in
situ VFOA estimation capabilities to enable robots to adapt in the specific
scenarios. However, we believe that off-line pattern identification can lead to
a better understanding of the children progression as well as engagement level
assessment in face-to-face long term interactions.

@@

\section{Attention Assessment}

@@

The presented method have been successfully employed in a real child-robot
interaction situation where the robot tries to engage the child in handwriting
tasks using learning by teaching paradigm.

@@

In this work, head orientation is used to predict a person's focus of attention
in face-to-face interactions. Therefore, we assume that head pose is a reliable
marker of the attention focus during a social interaction, in both cases
human-human, human-robot. Since we estimate where the subject is looking at
based on its head position, several important questions arise:

\begin{enumerate}
\item Which head pose estimation tracking rate can we achieve during a real case scenario?  
\item How accurate can we predict where the subject is looking at based on the head pose estimation?
\item How can we evaluate the engagement of the children based on the focus of attention?\newline
\end{enumerate}

>>>>

We predict that there will be no generalizable pattern of participant's VFOA
behavior for different scenarios such as multiple subjects, necessitating in
situ VFOA estimation capabilities to enable robots to adapt in the specific
scenarios. However, we believe that off-line pattern identification can lead to
a better understanding of the children progression as well as engagement level
assessment in face-to-face long term interactions.\fixme{I did not understand
this paragraph}

\fixme{Underline difference between field of attention and focus of attention}

\fixme{State the hypothesis: head-pose estimation provides a good-enough
approximation of the gaze direction, and in turn of the field of attention, and
in turn of the focus of attention}

@@

\section{Visual Attention Assessment}

\subsection{Overview of the Technique}

@@

As presented above, we use the (6D) head pose as an approximation of the
actual gaze direction, and we approximate from here the participant's field of
attention. The assumption that such an approximation of the field of attention
allows to derive the actual focus of attention is the core hypothesis that we
ought to validate.

This section presents such an experimental validation, set in the context of a
real child-robot interaction scenario where the robot tries to engage a child in
handwriting tasks using learning by teaching paradigm.

@@
